\section{Preface}
Cryptographic currencies and decentralized blockchain environments are increasingly pervading industries and society, but still not massively adopted nor in general use. In addition, crypto projects have not typically focused on the mobile environment and privacy is considered a `nice to have' feature.

ODIN aims to address all these concerns. It will do this by:
\begin{itemize}
   \item building a mobile-focused development platform 
   \item creating decentralized applications (Dapps) built on this platform
   \item having privacy as a core feature.
\end{itemize}

The core of ODIN is its community. ODIN will focus on four main communities: the infrastructure community, the Dapps community, the end user community and the entrepreneurial community; all of which require their own information and have different motivations and needs.
\begin{itemize}
\item A committed infrastructure community will provide the backbone of masternodes and staking wallets to ensure resilience, agility and function
\item The Dapps community will provide development in the form of applications to be run by the `end user' community
\item The end user community is our target audience. They download and use the applications built and running on the ODIN Blockchain
\item The entrepreneurial community are interested in ODIN's potential for creating a solution to a known problem and developing this into either a profitable business model or a not-for-profit solution for the common good. Much like the infrastructure community, this community could likely hold a large stake in the network.
\end{itemize}

Developing a Dapp community will help meet ever changing end user needs by creating decentralized applications to enable growth into areas of society where blockchain solutions are needed but not yet provided. One way this Dapp community will be supported is with a range of instructional toolkits and additional support functions. Usability will be at the forefront of every decision, toolkit and tutorial we provide (see \hyperlink{solution}{The Solution}).

A large, diverse and vibrant end user community is the life blood of a utility oriented environment. Adoption patterns guide developers and the service fees resulting from their activity contribute towards the sustainability of the ecosystem as a whole.

The consequential impact of the previous three communities (infrastructure, end user and developer) will ensure continued investment and interest from the entrepreneurial community, and their continued interest in turn yields constant new interest and development within other communities.
